Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Renamed the \ide command
Easier to type this way

\newcommand{\croder}{\textsc{Croder }}
\newcommand{\IDE}{\emph{IDE }}
\newcommand{\eclipse}{\emph{Eclipse }}

@@

 \croder allows the programmer to easily choose snippets from many places in the \IDE. The reasoning behind this is that if a resource contains or points to code, \croder should be able to transform it into a snippet. Figure \ref{fig:snippetSelection} shows  various resources which \croder can convert to code snippets, such as random editor selections, fields, methods and whole classes. As can be seen, resources originate from diverse views.

@@

In terms of the current implementation, particular code reviews are tied to only one \IDE installation. The feature to share and access the review results with other colleague's \IDE's would be most welcome.

Last but not least, code reviews represent only one possible software development task that can be crowdsourced. We identified several more, such as testing or on demand code transformations. In order to fully bring the knowledge of the crowds into the \IDE, \croder will have to learn how to crowdsource many more tasks, starting with the ones previously mentioned.

>>>>

\newcommand{\croder}{\textsc{Croder }}
\newcommand{\ide}{\emph{IDE }}
\newcommand{\eclipse}{\emph{Eclipse }}

@@

 \croder allows the programmer to easily choose snippets from many places in the \ide. The reasoning behind this is that if a resource contains or points to code, \croder should be able to transform it into a snippet. Figure \ref{fig:snippetSelection} shows  various resources which \croder can convert to code snippets, such as random editor selections, fields, methods and whole classes. As can be seen, resources originate from diverse views.

@@

In terms of the current implementation, particular code reviews are tied to only one \ide installation. The feature to share and access the review results with other colleague's \ide's would be most welcome.

Last but not least, code reviews represent only one possible software development task that can be crowdsourced. We identified several more, such as testing or on demand code transformations. In order to fully bring the knowledge of the crowds into the \ide, \croder will have to learn how to crowdsource many more tasks, starting with the ones previously mentioned.
